---
title: "MN GOTV 2017: Randomization Code"
author: "Anna Cooper"
date: "`r Sys.time() - 60 * 60 * 5`"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width = 6, fig.height = 3.5)
aiHelper::check_packages()
```

```{r config, echo = T, message=FALSE, warning=FALSE}
library(aiRando)
library(aiHelper)
library(ggplot2)
library(data.table)
rm(list = ls())
```

[Here is a link to randomization plan](www.linkhere.com).

# Config {.tabset}

## Set Seed 

```{r}
set.seed(42991)
```

## Configure Randomization

<!-- If you need to rename/recode variables or create unique ID,  -->
<!-- do that in basefile. -->

<!-- If you need to subset using roboscreen data, you should have a returned  -->
<!-- roboscreen that you can match into the basefile by unique ID or phone number. -->

<!-- After you read in data, subset to only the data that you need. -->

Data Input

```{r data input, echo = T}
# Read in Data
wd <- "C:/Users/acooper/Documents/Experiments/MN GOTV 2017/"
df <- aiHelper::read_in(file.path(wd, "mn_joint_gotv.csv"))

# Name of your unique id
unique_id <- "voterfilevanid"

df <- df[order(df$voterfilevanid), ]
```


Data Export

````{r}
# Folder where randomization should be stored
rand_loc <- file.path(wd,"randomization")
```

Variables

```{r}
df$x_2016catpartisan <- aiHelper::ai_impute(df$x_2016catpartisan, verbose = T)
df$partisan_bin <- aiHelper::apply_quantiles(df$x_2016catpartisan, breaks = 3)

df$x_2017catvprop <- aiHelper::ai_impute(df$x_2017catvprop, verbose = T)
df$turnout_bin <- aiHelper::apply_quantiles(df$x_2017catvprop, breaks = 3)

df[df$sex=='U',]$sex <- 'F'

# Stratification variables
strat_vars <- c("age", "racename", "sex","partisan_bin","turnout_bin","age","countyname")

# Balance variables
bal_vars <- strat_vars

# Creative Fields
creative_fields <- c("firstname","lastname","suffix","maddress","mcity","mstate","mzip5") 

df <- df[, unique(c('voterfilevanid', strat_vars, bal_vars, creative_fields))]

# Set Treatment Groups
# General best practice is to perform a single randomization
# No matter how many treatment groups/types you have

```

<!-- ## Create Necessary Folders -->

<!-- ```{r, render = F} -->

<!-- if( !is.null(export_script) && !file.exists(export_script)){ -->
<!--     stop("mn_rando_script") -->
<!-- } -->

<!-- if(! dir.exists(rand_loc)){ -->
<!--   cat(sprintf("C:/Users/acooper/Documents/Experiments/MN GOTV 2017/", rand_loc)) -->
<!--   dir.create(rand_loc) -->
<!-- } -->
<!-- ``` -->


<!-- SHOULD NOT HAVE TO EDIT BELOW HERE FOR MOST RANDOMIZATIONS -->
<!-- EXPORT FILE IS SEPARATE -->

# Subset to Required Fields

```{r}
default_fields <- unique(
  c('voterfilevanid', unique_id, 'mstate', strat_vars, bal_vars, creative_fields))

not_in <- default_fields[!default_fields %in% names(df)]

if(!is.null(not_in)){
  sprintf("NOTE: The variables %s are in default fields but are not in your df.", 
          not_in)
}

df <- df[, names(df) %in% default_fields]
```

# Checks {.tabset}

Check for uniqueness of ids and nonmissing on essential covariates (names, 
addresses, etc). If there are missings, maybe a good idea to go back and impute
on the basefile.

## No Missing 

```{r}
aiHelper::check_df(df)
```

## IDs, etc.

```{r}
#aiHelper::check_ids(df, voterfile_id = "voterfilevanid",)
```

## Distributions

```{r}
aiHelper::print_distrib(df, unique(c(strat_vars, bal_vars)))
```

# Randomize Treatment Groups

```{r single_rand, echo = T}
x <- aiRando::rand(dat = df,
                   treat_prop = c(1/3, 1/3, 1/3),
                   treat_labs = c('control', 'voting_rights', 
                                  'social_pressure'),
                   assign_var = 'final_assign',
                   strat_vars = strat_vars,
                   bal_vars = bal_vars,
                   subset = F)
```

## Final Assignment

Create the final assignment variable

```{r treatment, echo = T}
# Check distribution of final assignment

aiHelper::ai_table(x$final_assign, ptable = T)
```

## Internal

Exporting skinny file of the ids, treatments, and strata as well as full internal dataset.

```{r export}

time_exp <- format(Sys.time(), "%Y%m%d_%H%M%S")

aiHelper::export_csv(df, 
                     filename = paste0(wd, "mn_rando.csv"))


# full_name <- paste0(time_exp, 'mn_gotv_full_randomization.txt')
# aiHelper::export_tab(df, filename = file.path(rand_loc, full_name))
```
